% PREAMBLE
%%%%%%%%%%
%%%%%%%%%%

\documentclass[oneside,a4paper]{scrartcl}

% PACKAGES
%%%%%%%%%%
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{pgf}
\usepackage{placeins}
\usepackage{listings}


% DOCUMENT
%%%%%%%%%%
%%%%%%%%%%

\begin{document}

%%%%%%%
% TITLE
%%%%%%%

\title{Exercise Sheet VIII}
\subject{Advanced Parallel Computing}
\author{Klaus Naumann \& Christoph Klein}
\maketitle

%%%%%%%
% PART 1 - Reading
%%%%%%%
\section*{Reading}
\subsection*{First Paper}
The paper 'The AMD Opteron Northbridge Architecture' from Pat Conway and Bill Hughes
published in 2007 presents an improved Northbridge architecture realized by AMD's
Direct Connect architecture, which uses an industry-standard HyperTransport technology
to link the processors with each other.

The main advantages of a HyperTransport interconnection are scalability, a high
bandwidth and wol latency. Furthermore the Direct Connect architecture provides
on chip integrated memory controller, thus reducing the front side bus bottlenecks.
The implemented HyperTransport protocol (HTP) ensures a coherent shared memory address
space. The HTP uses a broadcast-based coherence protocol, thus supports a good scaling
up to an eight-socket. Moreover this architecture has a lower power consumption
in comparison to the front side bus architecture.

To our mind this paper presents a detailed technical view on the new Northbridge
architecture, thus it provides useful information for the system architect, but not for
the system user. We would accept this paper, because sharing system architecture information
supports/accelerates system architecture developement.



\end{document}
